Stack Safety as a Security Property

### 2020-07-09 main.tex
Polishing section 2

To streamline the exposition of the example, we use a small instruction set
reminiscent of RISC-V and make few simplifying assumptions.
%
First, since our goal is to formalize stack safety, we ignore the heap and
assume that the memory is divided between the instructions and the stack.
(Integrating a memory safety property for the heap in the style of
\citet{AzevedoDeAmorim17} is a natural extension that we discuss
in~\Cref{sec:future}.)
%
We also abstract away low-level details of memory layout and assume a
machine that is word- (not byte-) addressed, with instructions starting from
location 0, a dedicated memory-mapped output port at location 99, and
the stack beginning at location 100 and growing upwards with increasing
addresses.  \leo{Explain more? How to connect to realistic
  one? Observations? DMA? Interrupt handlers?}\bcp{Yes.}

@@

Stack safety is meant to protect a caller from a malicious callee's
attempts to access private data or highjack its control flow. Our
attacker model reflects this intention: we assume that the attacker
can run arbitrary code as a caller and the enforcement mechanism
should protect against that. Hardware and timing attacks are out of
scope. \leo{Anything else to add here?}
\leo{Maybe a good place to discuss calling conventions and that they
  are essentially enforced by the policy or sth?}
\rb{Intuition that the callee can do anything in principle, but the machine will
halt if it does not follow the calling convention, etc.?}

>>>>

To streamline the example, we use a small instruction set reminiscent of
RISC-V and make a few simplifying assumptions about the organization of
memory.
%
First, since our goal is to formalize stack safety, we ignore the heap and
assume that the memory is divided between the instructions and the stack.
(Integrating a memory safety property for the heap in the style of
\citet{AzevedoDeAmorim17} is a natural extension that we discuss
in~\Cref{sec:future}.)
%
We also assume that the machine is word- (not byte-) addressed, that program
instructions start from location 0, that the machine communicates with the
outside world through a single memory-mapped output port at address 99, and that the stack begins at location 100 and grows upwards.
% \leo{Explain more?  How to connect to realistic one? Observations? DMA?
%   Interrupt handlers?}\bcp{Yes.}

@@

Stack safety is meant to protect a caller from a confused or malicious callee's
attempts to access private data or highjack its control flow. Our
attacker model reflects this intention by assuming that the attacker
can run arbitrary code to try to access or overwrite its caller's stack data
or disrupt its control state. Hardware and timing attacks are out of
scope. \leo{Anything else to add here?}
\leo{Maybe a good place to discuss calling conventions and that they
  are essentially enforced by the policy or sth?}
\rb{Intuition that the callee can do anything in principle, but the machine will
halt if it does not follow the calling convention, etc.?}
